### 2021-07-31 doc/src/MSLevel.tex
Rename "operating mode" to "privilege mode"

As established by the {\RISCV} Privileged Architecture, an interrupt
traps to \mbox{M-mode} whenever all of the following are true:
(a)~either the current operating mode is \mbox{M-mode} and
machine-level interrupts are enabled by the MIE bit of \z{mstatus}, or
the current operating mode has less privilege than \mbox{M-mode};
(b)~matching bits in \z{mip}/\z{miph} and \z{mie}/\z{mieh} are both
one; and
(c)~if \z{mideleg} exists, the corresponding bit in
\z{mideleg}/\z{midelegh} is zero.

@@

Just as for machine level, the taking of interrupt traps at supervisor
level remains essentially the same as specified by the {\RISCV}
Privileged Architecture.
An interrupt traps into \mbox{S-mode} (or \mbox{HS-mode}) whenever all
of the following are true:
(a)~either the current operating mode is \mbox{S-mode} and
supervisor-level interrupts are enabled by the SIE bit of \z{sstatus},
or the current operating mode has less privilege than \mbox{S-mode};
(b)~matching bits in \z{sip}/\z{siph} and \z{sie}/\z{sieh} are both
one, or, if the hypervisor extension is implemented, matching bits in
\z{hip} and \z{hie} are both one; and
(c)~if the hypervisor extension is implemented, the corresponding bit
in \z{hideleg}/\z{hidelegh} is zero.

>>>>

As established by the {\RISCV} Privileged Architecture, an interrupt
traps to \mbox{M-mode} whenever all of the following are true:
(a)~either the current privilege mode is \mbox{M-mode} and
machine-level interrupts are enabled by the MIE bit of \z{mstatus}, or
the current privilege mode has less privilege than \mbox{M-mode};
(b)~matching bits in \z{mip}/\z{miph} and \z{mie}/\z{mieh} are both
one; and
(c)~if \z{mideleg} exists, the corresponding bit in
\z{mideleg}/\z{midelegh} is zero.

@@

Just as for machine level, the taking of interrupt traps at supervisor
level remains essentially the same as specified by the {\RISCV}
Privileged Architecture.
An interrupt traps into \mbox{S-mode} (or \mbox{HS-mode}) whenever all
of the following are true:
(a)~either the current privilege mode is \mbox{S-mode} and
supervisor-level interrupts are enabled by the SIE bit of \z{sstatus},
or the current privilege mode has less privilege than \mbox{S-mode};
(b)~matching bits in \z{sip}/\z{siph} and \z{sie}/\z{sieh} are both
one, or, if the hypervisor extension is implemented, matching bits in
\z{hip} and \z{hie} are both one; and
(c)~if the hypervisor extension is implemented, the corresponding bit
in \z{hideleg}/\z{hidelegh} is zero.

### 2021-07-31 doc/src/VSLevel.tex
Rename "operating mode" to "privilege mode"

When the hypervisor extension is implemented, a hart's set of possible
operating modes includes the \emph{virtual supervisor} (VS) and
\emph{virtual user} (VU) modes for hosting virtual harts.
The Advanced Interrupt Architecture adds to the hypervisor extension
new interrupt facilities aligned with those described earlier for
supervisor-level interrupts.

@@

Whenever the value of CSR \z{vstopi} is not zero, if either the current
operating mode is \mbox{VS-mode} and the SIE bit in CSR \z{vsstatus}
is set, or the current operating mode is \mbox{VU-mode}, a trap is
taken to \mbox{VS-mode} for the interrupt indicated by field IID of
\z{vstopi}.

>>>>

When the hypervisor extension is implemented, a hart's set of possible
privilege modes includes the \emph{virtual supervisor} (VS) and
\emph{virtual user} (VU) modes for hosting virtual harts.
The Advanced Interrupt Architecture adds to the hypervisor extension
new interrupt facilities aligned with those described earlier for
supervisor-level interrupts.

@@

Whenever the value of CSR \z{vstopi} is not zero, if either the current
privilege mode is \mbox{VS-mode} and the SIE bit in CSR \z{vsstatus}
is set, or the current privilege mode is \mbox{VU-mode}, a trap is
taken to \mbox{VS-mode} for the interrupt indicated by field IID of
\z{vstopi}.
